Legion: Expressing Locality and Independence with Logical Regions

### 2012-08-04 doc/sc2012/legion.tex
Adding some stuff for the final version of the SC paper

\documentclass[conference]{IEEEtran}

\bibliographystyle{IEEEtran}
\usepackage{amsmath,amsthm}
\usepackage{listings}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{booktabs}
\usepackage{dcolumn}
\usepackage{cancel}
\usepackage{graphics}
\usepackage{url}

@@

\title{Legion: Expressing Locality and Independence with Logical
  Regions\thanks{This work was supported by the Army High Performance
    Research Center (DARPA contract HR0011-10-9-0008), a subcontract
    from Los Alamos National Laboratory for the DOE Office of Science,
    Advanced Scientific Computing Research (DE-AC52-06NA25396), and NVIDIA.  The views and
    conclusions contained in this document are those of the authors
    and should not be interpreted as representing the official
    policies, either expressed or implied, of the U.S. Government.}}
\author{ \IEEEauthorblockN{Michael Bauer\IEEEauthorrefmark{1},
%\authorinfo(Stanford University, email: \mbox{mebauer@cs.stanford.edu}
Sean Treichler\IEEEauthorrefmark{1}, 
%\authorinfo(Stanford University, email: \mbox{sjt@cs.stanford.edu}
Elliott Slaughter\IEEEauthorrefmark{1}, 
% \authorinfo(Stanford University, email: \mbox{slaughter@cs.stanford.edu}
Alex Aiken\IEEEauthorrefmark{1}  
%\authorinfo(Stanford University, email: \mbox{aiken@cs.stanford.edu}
%\email{aiken@cs.stanford.edu}
}
\IEEEauthorblockA{
\IEEEauthorrefmark{1}{Computer Science Department, Stanford University}
}
}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts 
\bibliographystyle{IEEEtran}
\usepackage{amsmath,amsthm}
\usepackage{listings}
\usepackage{tikz}
\usepackage{subfigure}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{booktabs}
\usepackage{dcolumn}
\usepackage{cancel}
\usepackage{graphics}
\usepackage{url}
\usepackage{minibox}

@@

\title{Legion: Expressing Locality and Independence with Logical
  Regions\thanks{This work was supported by the Army High Performance
    Research Center (DARPA contract HR0011-10-9-0008), a subcontract
    from Los Alamos National Laboratory for the DOE Office of Science,
    Advanced Scientific Computing Research (DE-AC52-06NA25396), and NVIDIA.  The views and
    conclusions contained in this document are those of the authors
    and should not be interpreted as representing the official
    policies, either expressed or implied, of the U.S. Government.}}
%\author{ \IEEEauthorblockN{Michael Bauer\IEEEauthorrefmark{1},
%%\authorinfo(Stanford University, email: \mbox{mebauer@cs.stanford.edu}
%Sean Treichler\IEEEauthorrefmark{1}, 
%%\authorinfo(Stanford University, email: \mbox{sjt@cs.stanford.edu}
%Elliott Slaughter\IEEEauthorrefmark{1}, 
%% \authorinfo(Stanford University, email: \mbox{slaughter@cs.stanford.edu}
%Alex Aiken\IEEEauthorrefmark{1}  
%%\authorinfo(Stanford University, email: \mbox{aiken@cs.stanford.edu}
%%\email{aiken@cs.stanford.edu}
%}
%\IEEEauthorblockA{
%\IEEEauthorrefmark{1}{Computer Science Department, Stanford University}
%}
%}

\author{
\IEEEauthorblockN{Michael Bauer}
\IEEEauthorblockA{Stanford University \\ mebauer@cs.stanford.edu}
\and
\IEEEauthorblockN{Sean Treichler}
\IEEEauthorblockA{StanfordUniversity \\ sjt@cs.stanford.edu}
\and
\IEEEauthorblockN{Elliott Slaughter}
\IEEEauthorblockA{Stanford University \\ slaughter@cs.stanford.edu}
\and
\IEEEauthorblockN{Alex Aiken}
\IEEEauthorblockA{Stanford University \\ aiken@cs.stanford.edu}
}

\IEEEpubid{\makebox[\columnwidth][l]{\minibox{SC12, November 10-16, 2012, Salt Lake City, Utah, USA \\ 978-1-4673-0806-9/12/ \$31.00~\copyright~2012 IEEE}}
\hspace{\columnsep}
\makebox[\columnwidth]{}
}
